---
title: Legacy sites and GRTS
output:
  xaringan::moon_reader:
  #  self_contained: TRUE
    includes:
      in_header: conf/style-header.html
    lib_dir: assets
    seal: false
    css: ["default", "conf/css/style.css", "conf/css/fonts.css"]
    nature:
      highlightStyle: solarized-light
      highlightLines: true
      beforeInit: ["conf/js/gifffer.min.js", "conf/js/style-macros.js"]
---

```{r setup, echo = F}
knitr::opts_chunk$set(
  comment = "#",
  #cache = TRUE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 5.25,
  fig.align = 'center',
  fig.retina = 3
)

# base plot layout
mypar = list(mar = c(3,3,0.5,0.5), mgp = c(1.5, 0.3, 0), tck = -.008)

# xaringan Extra
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_panelset()
```
class: middle, title-slide

<!-- top logo (comment to remove or edit on `conf/css/style.css:23`) -->
<div class="lab-logo"></div>
<!-- <div class="uni-logo"></div> -->

# Title of my talk template

<hr width="65%" align="left" size="0.3" color="orange"></hr>

## Legacy sites & GRTS

### Willian Vieira

<br><br><br><br><br>
[<i class="fa fa-github fa-lg" style="color:#e7e8e2"></i> WillVieira/talkTemplate](https://github.com/willvieira/talk_adjLegacySites)

[<i class="fa fa-twitter fa-lg" style="color:#e7e8e2"></i> @WillVieira90](https://twitter.com/willvieira90)


---
# Why do we need to adjust sample size?

```{r, message=FALSE, echo = F,cache=TRUE}
source('R/prepare_hex.R')
```

```{r run GRTS, echo = FALSE}
set.seed(0)

Stratdsgn = c('eco_101S' = 114)

sampleFrame <- hexas %>%
        mutate(    
            eco_name = paste0('eco_', ecoregion), # to match design name
            mdcaty  = sum(Stratdsgn) * p/sum(p),
            geometry = sf::st_geometry(sf::st_centroid(geometry))
        )      

out_sample <- spsurvey::grts(
    sframe = sampleFrame,
    n_base = Stratdsgn,
    stratum_var = 'eco_name',
    aux_var = 'mdcaty'
)
```

Ecoregion 101S

```{r,echo=FALSE,fig.width=9,fig.height=7}
ggplot() +
    geom_sf(data = st_union(subset(hexas, ecoregion == '101S'))) +
    ggtitle('Sample size = 114')
```

---
# Why do we need to adjust sample size?

Ecoregion 101S + <span style="color:red">GRTS</span>

```{r,echo=FALSE,fig.width=9,fig.height=7}
ggplot() +
    geom_sf(data = st_union(subset(hexas, ecoregion == '101S'))) +
    geom_sf(data = subset(hexas, ET_Index %in% out_sample$sites_base$ET_Index), fill = 'red', color = 'transparent') + 
    ggtitle('Sample size = 114')
```

---
# Why do we need to adjust sample size?

Ecoregion 101S + <span style="color:red">GRTS</span> +  <span style="color:rgba(130, 137, 235)">legacy sites</span>

```{r,echo=FALSE,fig.width=9,fig.height=7}
ggplot() +
    geom_sf(data = st_union(subset(hexas, ecoregion == '101S'))) +
    geom_sf(data = subset(hexas, ET_Index %in% out_sample$sites_base$ET_Index), fill = 'red', color = 'transparent') +
    geom_sf(data = subset(hexas, ecoregion == '101S' & legacySite > 0), fill = 'blue', color = 'transparent', alpha = 0.5) +
    ggtitle('Sample size = 114; Legacy sites = 1033')
```


---
# Why do we need to adjust sample size?

Ecoregion 101S + <span style="color:red">GRTS</span> (adjusted *p*) +  <span style="color:rgba(130, 137, 235)">legacy sites</span>

```{r,echo=FALSE,fig.width=9,fig.height=7,cache=TRUE}

# Coordinates of all hexagons in matrix format for MBHdesign
coord_mt <- sampleFrame %>%
    st_coordinates()

# Coordinates of legacy hexagons
legacySites <- sampleFrame %>%
    filter(legacy > 0) %>%
    st_coordinates()

sampleFrame$adj_p <- MBHdesign::alterInclProbs(
    legacy.sites = legacySites,
    potential.sites = coord_mt,
    inclusion.probs = sampleFrame$mdcaty,
    sigma = 10000
)

out_sample_adjP <- spsurvey::grts(
    sframe = sampleFrame,
    n_base = Stratdsgn,
    stratum_var = 'eco_name',
    aux_var = 'adj_p'
)
```
```{r,echo=FALSE,fig.width=9,fig.height=7,cache=TRUE}
ggplot() +
    geom_sf(data = st_union(subset(hexas, ecoregion == '101S'))) +
    geom_sf(data = subset(hexas, ET_Index %in% out_sample_adjP$sites_base$ET_Index), fill = 'red', color = 'transparent')+
      geom_sf(data = subset(hexas, ecoregion == '101S' & legacySite > 0), fill = 'blue', color = 'transparent', alpha = 0.5) + 
    ggtitle('Sample size = 114; Legacy sites = 1033')
```


---
# Why do we need to adjust sample size?

Ecoregion 217 + <span style="color:rgba(130, 137, 235)">legacy sites</span>

```{r,echo=FALSE,fig.width=9,fig.height=7,cache=TRUE}

Stratdsgn = c('eco_217' = 46)

sampleFrame <- hexas %>%
        mutate(    
            eco_name = paste0('eco_', ecoregion), # to match design name
            mdcaty  = sum(Stratdsgn) * p/sum(p),
            geometry = sf::st_geometry(sf::st_centroid(geometry))
        )      

out_sample <- spsurvey::grts(
    sframe = sampleFrame,
    n_base = Stratdsgn,
    stratum_var = 'eco_name',
    aux_var = 'mdcaty'
)
# Coordinates of all hexagons in matrix format for MBHdesign
coord_mt <- sampleFrame %>%
    st_coordinates()

# Coordinates of legacy hexagons
legacySites <- sampleFrame %>%
    filter(legacy > 0) %>%
    st_coordinates()

sampleFrame$adj_p <- MBHdesign::alterInclProbs(
    legacy.sites = legacySites,
    potential.sites = coord_mt,
    inclusion.probs = sampleFrame$mdcaty,
    sigma = 10000
)

out_sample_adjP <- spsurvey::grts(
    sframe = sampleFrame,
    n_base = Stratdsgn,
    stratum_var = 'eco_name',
    aux_var = 'adj_p'
)
```


```{r,echo=FALSE,fig.width=9,fig.height=7,cache=TRUE}
ggplot() +
    geom_sf(data = st_union(subset(hexas, ecoregion == '217'))) +
    geom_sf(data = subset(hexas, ecoregion == '217' & legacySite > 0), fill = 'blue', color = 'transparent', alpha = 0.5) + 
    ggtitle('Sample size = 46; Legacy sites = 96')
```

---
# Why do we need to adjust sample size?

Ecoregion 217 + <span style="color:red">GRTS</span> (adjusted *p*) + <span style="color:rgba(130, 137, 235)">legacy sites</span>

```{r,echo=FALSE,fig.width=9,fig.height=7,cache=TRUE}
ggplot() +
    geom_sf(data = st_union(subset(hexas, ecoregion == '217'))) +
    geom_sf(data = subset(hexas, ET_Index %in% out_sample_adjP$sites_base$ET_Index), fill = 'red', color = 'transparent')+
      geom_sf(data = subset(hexas, ecoregion == '217' & legacySite > 0), fill = 'blue', color = 'transparent', alpha = 0.5) + 
    ggtitle('Sample size = 46; Legacy sites = 96')
```

---
class: middle, center, inverse

# How to adjust sample size in function of the number and spatial distribution of legacy sites?

<hr width="100%" align="left" size="0.3" color="orange"></hr>


---

```{r,echo=FALSE,cache=TRUE}
sfc = st_sfc(st_polygon(list(rbind(c(0,0), c(8,0), c(8,8), c(0,0)))))
fake_hex <- st_make_grid(sfc, cellsize = .1, square = FALSE)
set.seed(3)
legacy <- fake_hex[sample(1:length(fake_hex), 20)]

```


```{r,echo=FALSE,cache=TRUE,fig.width=12,fig.height=9}
ggplot(fake_hex) +
    geom_sf() +
    geom_sf(data = legacy, fill = 'red', color = 'transparent') +
    ggtitle('Sample size = 153; Legacy sites = 20')
```

---

```{r,echo=FALSE,cache=TRUE,fig.width=12,fig.height=9}
ggplot(fake_hex) +
    geom_sf() +
    geom_sf(data = legacy, fill = 'red', color = 'transparent') +
    geom_sf(data = st_union(st_buffer(legacy, dist = 0.7)), fill = 'red', color = 'transparent', alpha = .5) +
    ggtitle('Sample size = 153; Legacy sites = 20')

```

---

Ecoregion 101S

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}
hexas_eco <- hexas %>%
  filter(ecoregion == '101S')

ggplot() +
  geom_sf(data = st_union(hexas_eco)) +
  geom_sf(data = st_union(st_buffer(subset(hexas_eco, legacySite > 0), dist = 19000)), fill = 'red', color = 'transparent', alpha = 0.4) +
  geom_sf(data = subset(hexas_eco, legacySite > 0), fill = 'red', color = 'transparent') +
  ggtitle('Initial sample size = 114; Legacy sites = 1033; Adjusted sample size = 0')
```

---

Ecoregion 101S

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}

hexas_eco <- hexas %>%
  filter(ecoregion == '217')

ggplot() +
  geom_sf(data = st_union(hexas_eco)) +
  geom_sf(data = st_union(st_buffer(subset(hexas_eco, legacySite > 0), dist = 19000)), fill = 'red', color = 'transparent', alpha = 0.4) +
  geom_sf(data = subset(hexas_eco, legacySite > 0), fill = 'red', color = 'transparent') +
  ggtitle('Initial sample size = 46; Legacy sites = 96; Adjusted sample size = 28')
```

---
class: middle, center, inverse

# How do we define the optimum buffer size?

<hr width="100%" align="left" size="0.3" color="orange"></hr>


---

96 selected hexagons from GRTS

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}

hexas_eco <- hexas %>%
  filter(ecoregion == '217')

ggplot() +
  geom_sf(data = st_union(hexas_eco)) +
  geom_sf(data = subset(hexas, ET_Index %in% out_sample$sites_base$ET_Index), fill = 'black', color = 'transparent')
```

---

96 selected hexagons from GRTS; <span style="color:red">48 sampled</span>;  <span style="color:rgba(130, 137, 235)">48 non-sampled</span>

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}

sel <- subset(hexas, ET_Index %in% out_sample$sites_base$ET_Index)
selected <- sample(1:nrow(sel), round(nrow(sel)/2, 0))
sel_year1 <- sel[selected, ]
sel_year1b <- sel[!(1:nrow(sel) %in% selected), ]

ggplot() +
  geom_sf(data = st_union(hexas_eco)) +
  geom_sf(data = sel_year1, fill = 'red', color = 'transparent') +
  geom_sf(data = sel_year1b, fill = 'blue', color = 'transparent', alpha = 0.5)
```


---

What would be the optimum buffer size so the adjusted sample is equal to <span style="color:rgba(130, 137, 235)">48</span>?

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}

sel <- subset(hexas, ET_Index %in% out_sample$sites_base$ET_Index)
selected <- sample(1:nrow(sel), round(nrow(sel)/2, 0))
sel_year1 <- sel[selected, ]
sel_year1b <- sel[!(1:nrow(sel) %in% selected), ]

ggplot() +
  geom_sf(data = st_union(hexas_eco)) +
  geom_sf(data = sel_year1, fill = 'red', color = 'transparent') +
  geom_sf(data = sel_year1b, fill = 'blue', color = 'transparent', alpha = 0.5) +
  geom_sf(data = st_union(st_buffer(sel_year1, dist = 18000)), fill = 'red', color = 'transparent', alpha = 0.3)
```

---

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}
bufferSize <- readRDS('../samplingBMS/bufferSize.RDS')

bufferSize %>%
      mutate(sizeProp = as.factor(sizeProp)) %>% 
      ggplot(aes(x = optSize, y = ecoregion)) + 
          ggridges::geom_density_ridges(alpha = 0.3) + 
          theme_classic()

```

---

```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=8}
bufferSize %>% 
  ggplot(aes(sizeProp, optSize)) +
  geom_point(alpha = .2) +
  geom_smooth() +
  facet_wrap(~ecoregion)
```



